*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-21 Code/Manuscript_O2.Rmd
Added a bit more to protein materila and methods

Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 uL of 1X protein extraction buffer (0.0281 mol L^−1 TRIS base buffer, 0.0211 mol L^−1 TRIS HCl buffer, 0.0735 mol L^−1 lithium dodecyl sulfate, 1.08 mol L^−1 glycerol, 0.5 mmol L^−1 ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) [@brownFluxCapacitiesAcclimation2008]  XXX note we used a low tris PEB recipe not sure where it came from XXX. Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.  The lysing vials were centrifuged at 16100g for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.  40 µL of the supernatant were subsampled into labeled vials and stored at -80 °C until analysis. The bicinchoninic acid (BCA) assay was used for total protein determination using a calibration curve of bovine gamma globulin (BGG; Bio-Rad, Hercules, CA, USA) standard ranging from 0 to 1.0 mg mL^-1 range.

All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008]. Between 0.1 to 4.0 µg of total protein was loaded onto 15 well Invitrogen Bolt 4-12% acrylamide Bis-Tris gels (ThermoFisher Scientific, Waltham, MA, USA). All gels were run for 25 minutes at 200V using Invitrogen Bolt Mini Gel tanks and Invitrogen Bolt MES SDS running buffer (ThermoFisher Scientific, Waltham, MA, USA) and transferred for 60 minutes at 20V onto a PVDF membrane (Bio-Rad, Hercules, CA, USA; SKU 1620177).  Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008. The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, ASXXXXX; PsaC 1:XXXXXX dilution, ASXXXXXXX ; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).  Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA). Images were quantitated using the ImageJ2 software (version 1.53c).

# Results and Discussion {.unnumbered}

@@

XXXX Mireille to finish Fig. caption  XXX
```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

@@

XXXX Mireille to finish Fig. caption  XXX
```{r MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",

>>>>

Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 uL of 1X protein extraction buffer (0.0281 mol L^−1^ TRIS base buffer, 0.0211 mol L^−1^ TRIS HCl buffer, 0.0735 mol L^−1^ lithium dodecyl sulfate, 1.08 mol L^−1^ glycerol, 0.5 mmol L^−1^ ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) [@brownFluxCapacitiesAcclimation2008]  XXX note we used a low tris PEB recipe not sure where it came from (citation??) XXX. Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.  The lysing vials were centrifuged at 16100g using XXXXXX centrifuge ( reference here    ) for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes. 40 µL of the supernatant were subsampled into labeled vials and stored at -80 °C until analysis. The bicinchoninic acid (BCA) assay was used for total protein determination using a calibration curve of bovine gamma globulin (BGG; Bio-Rad, Hercules, CA, USA) standard ranging from 0 to 1.0 mg mL^-1^ range.

All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008]. Standards were obtained from Agrisera (Vännäs, Sweden; FtsH AS11 1789S; PsbA AS01 016S; PetC AS08 330S; PsaC AS04 042S; RbcL AS01 017S).  Between 0.1 to 4.0 µg of total protein was loaded onto 15 well Invitrogen Bolt 4-12% acrylamide Bis-Tris gels (ThermoFisher Scientific, Waltham, MA, USA). All gels were run for 25 minutes at 200V using Invitrogen Bolt Mini Gel tanks and Invitrogen Bolt MES SDS running buffer (ThermoFisher Scientific, Waltham, MA, USA) and transferred for 60 minutes at 20V onto a PVDF membrane (Bio-Rad, Hercules, CA, USA; SKU 1620177). Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008. The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, AS08 330; PsaC 1:XXXXXX dilution, AS10 939; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).  Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA). Images were quantitated using the ImageJ2 software (version 1.53c).

# Results and discussion {.unnumbered}

@@

XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

@@

XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
```{r MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",
                                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
                    "Numbers over each bar are fmole target protein per ug total protein.",
